### 2014-09-25 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Edits to mesh details; update mesh figure

The structure involved in this fire incident was a four-story residential building with a flat roof that consisted of a bitumen membrane. The exterior was primarily stucco with large windows on the top three stories on the rear side of the structure. The right side of the structure shared a common fire wall with another residential structure. The structure had a 17.73~m (58~ft) by 8.53~m (28~ft) footprint and a height of 5.9~m (19~ft), as shown in Fig.~\ref{fig:floor_plan}.

@@

As discussed in Section~\ref{sec:geometry}, the structure had exterior dimensions of 17.73~m (58~ft) by 8.53~m (28~ft) and a total height of 5.9~m (19~ft). To ensure adequately resolved fluid flow in and out of the structure, the computational domain was extended beyond the volume of the structure. The total volume of the computational domain was 17~m (56~ft) by 22~m (72~ft) by 13.6~m (45~ft). A grid resolution of 10~cm (3.9~in) was used, which resulted in a total of approximately 5.1 million computational cells. As a result, all of the input model geometry lengths, ventilation openings (holes, doors, and windows), and fire areas will snap to the nearest 10~cm. Figure~\ref{fig:SMV_exterior_grid} shows the front and rear sides of the structure rendered in Smokeview with the 10~cm mesh.

@@

The domain was divided into 16 meshes (each containing between 272,000 and 367,200 grid cells) that could be processed in parallel, which reduced the amount of required calculation time to approximately 3~days. Figure~\ref{fig:mult_mesh} shows the entire structure within the computational domain that has been divided into multiple meshes. Table~\ref{tab:model_parameters} shows a summary of the model input parameters for the simulations that were conducted as part of this study.

\begin{figure}[!ht]
\includegraphics[width=6.5in]{../Figures/SMV_Exterior_Meshes}
\caption[Rear-left side of the structure within the computational domain.]
{Rear-left side of the structure within the computational domain with multiple meshes.}
\label{fig:mult_mesh}
\end{figure}

>>>>

The structure involved in this fire incident was a four-story residential building with a flat roof that consisted of a bitumen membrane. The exterior was primarily stucco with large windows on the top three stories on the rear side of the structure. The right side of the structure shared a common fire wall with another residential structure. The structure had exterior dimensions of 8.53~m (28~ft) by 17.73~m (58~ft) and a height of 5.9~m (19~ft), as shown in Fig.~\ref{fig:floor_plan}.

@@

As discussed in Section~\ref{sec:geometry}, the structure had exterior dimensions of 8.53~m (28~ft) by 17.73~m (58~ft) and a total height of 5.9~m (19~ft). To ensure adequately resolved fluid flow in and out of the structure, the computational domain was extended beyond the volume of the structure. The dimensions of the computational domain were 11.5~m (38~ft) by 22~m (72~ft) by 13.6~m (45~ft). A grid resolution of 10~cm (3.9~in) was used, which resulted in a total of approximately 3.4 million computational cells. As a result, all of the input model geometry lengths, ventilation openings (holes, doors, and windows), and fire areas will snap to the nearest 10~cm. Figure~\ref{fig:SMV_exterior_grid} shows the front and rear sides of the structure rendered in Smokeview with the 10~cm mesh.

@@

The domain was divided into 16 meshes (each containing between 184,000 and 248,200 grid cells) that could be processed in parallel, which reduced the amount of required calculation time to approximately 3~days. Figure~\ref{fig:mult_mesh} shows the entire structure within the computational domain that has been divided into multiple meshes. Table~\ref{tab:model_parameters} shows a summary of the model input parameters for the simulations that were conducted as part of this study.

\begin{figure}[!ht]
\includegraphics[width=4.5in]{../Figures/SMV_Exterior_Meshes}
\caption[Rear-left side of the structure within the computational domain.]
{Rear-left side of the structure within the computational domain with multiple meshes.}
\label{fig:mult_mesh}
\end{figure}
